### 2012-02-02 docs/visualization/visualization.tex
add contourcompare.py

{\tt data\_processing/python\_plotfile} provide a simple commandline
tool for doing visualizations of 2-d \boxlib\ plotfiles, and slices
through 3-d \boxlib\ plotfiles.  The main driver is written in python
and uses a set of Fortran routines, compiled with {\tt f2py} to
interface with the plotfile data.  To use the routine, you will need
to have {\tt matplotlib} and {\tt f2py} installed.  On a machine
running Fedora linux, you can install these packages via
\begin{verbatim}
yum install python-matplotlib f2py
\end{verbatim}

The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.  A simple plot can be made via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``tfromp'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.  See Figure~\ref{fig:python}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

@@

>>>>

{\tt data\_processing/python\_plotfile} provide a simple commandline
tool for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

\subsection{\tt plotsinglevar.py}

{\tt plotsinglevar.py} does visualizations of 2-d \boxlib\ plotfiles,
and slices through 3-d \boxlib\ plotfiles.  A simple plot can be made
via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``tfromp'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.  See Figure~\ref{fig:python}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

@@

\subsection{\tt contourcompare.py}

{\tt contourcompare.py} takes 2 plotfiles and a variable as arguments
and plots contours of the 2 datasets on the same set of axes.  This is 
form comparisons of different runs.  Running the script with no parameters
will give the full list available options.
